Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-21 Ben_Manuscripts/Paper1/figures/xrd.tex
New images

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

  Nanostructured membrane materials have become increasingly popular for 
  aqueous separations applications such as desalination and biorefinement
  because they offer the ability to control membrane architecture at the
  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
  \begin{itemize}
    \item Most membrane-based aqueous separations of small molecules can 
    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
  \end{itemize}

  While RO and NF have seen many advances in the past few decades, they 
  are far from perfect separation technologies.
  \begin{itemize}
    \item \textit{RO membranes}
    \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
    tortuous and polydisperse diffusion pathways which leads to 
    inconsistent performance \cite{song_nano_2011}
    \item \textbf{High energy requirements} : Necessarily high feed pressures 
    drive up energy requirements which strains developing regions and
    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
    \item \textbf{Separation based on differences in solubility and diffusivity}:
    Moreover, designing RO membranes to achieve targeted separations of 
    specific solutes is nearly impossible because various solutes dissolve
    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
    \item At best, one can exploit these differences to create a functional
    selective barrier.
    \item \textit{NF membranes}
    \item NF was introduced as an intermediate between RO and ultrafiltration,
    having the ability to separate organic matter and salts on the order of 
    one nanometer in size.
    \item Larger and well-defined pores drive down energy requirements while
    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
    \item NF is often used as a precursor to reverse osmosis
    \item Unfortunately, NF membranes, like RO, are produced with a pore size 
    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
  \end{itemize}

  Nanostructured membranes can bypass many of the performance issues which
  plague traditional NF and RO membranes.
  \begin{itemize}
    \item \textbf{Tune size and functionality of building blocks} to control pore
    size and shape: One can accomplish targeted separations with high 
    selectivity by tuning shape, size and functionality of the molecular
    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
    \item As a result, solute rejecting pores can have their sizes tuned
    uniformly, resulting in \textbf{strict size cut-offs}.
    \item Entirely \textbf{different mechanisms} may govern transport in a given
    nanostructured material which can inspire novel separation techniques.
  \end{itemize}

  Development of nanostructured materials has been limited by the ability
  to synthesize and scale various fundamentally sound technologies.
  \begin{itemize}
    \item \textbf{Graphene sheets} are atomically thick which results in excellent
    permeability but defects during manufacturing severely impact 
    selectivity. \cite{cohen-tanugi_multilayer_2016}
    \item Molecular dynamics simulations of \textbf{carbon nanotubes} show
    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
    \item \textbf{Zeolites} have sub-nm pores with a narrow pore size 
    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
    however, experimental rejection was low and attributed to interstitial
    defects formed during membrane synthesis \cite{li_desalination_2004}
    \item There is a need for a scalable nanostructured membrane
  \end{itemize}

  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
  aqueous separation applications. 
  \begin{itemize}
    \item LLCs share the characteristic ability of nanostructured membrane
    materials to create \textbf{highly ordered structures} with the added benefits
    of \textbf{low cost} and synthetic techniques feasible for 
    \textbf{large scale production} \cite{feng_scalable_2014}
    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
    phase. The presence of small amounts of water results in the H\textsubscript{II} 
    phase.
    \item In both cases, monomers assemble into mesophases made of hexagonally
    packed, uniform size, cylinders with hydrophilic groups oriented inward
    towards the pore center and hydrophobic groups facing outward.
    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
    the monomer named Na-GA3C11 has been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
    \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
    aligned, resulting in a low flux membrane, slowing research in the field.
    \item In 2014, Feng et al. showed that the mesophases could be aligned 
    using a magnetic field with subsequent crosslinking to lock the structure
    in place \cite{feng_scalable_2014}
    \item In 2016, Feng et al. showed that the same result could be obtained 
    using a technique termed soft confinement \cite{feng_thin_2016}.
    \item Following this breakthrough, research into LLC membranes has been
    reinvigorated
  \end{itemize}

  A molecular level understanding of LLC membrane structure, enabled by molecular
  dynamics simulations, will provide guidelines to reduce the large chemical space
  available to design monomers for creation of separation-specific membranes.
  \begin{itemize}
%     \item LLCs are versatile and controllable with a \textbf{large chemical design
%     space} available for membrane design  %BJC: redundant
    \item  We do not yet understand how to reduce the effective pore size or 
    how to tune the chemical environment in the nanopores for effective water
    desalination or small organic molecule separations.
    \item Rejection studies show that this membrane can not perform separations of
    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
    \item Over the past 20 years, LLC membrane studies have been limited primarily 
    to Na-GA3C11 with some characterization done after minor structural modifications
    \cite{resel_structural_2000}. 
    \item Optimization has been performed through trial and error. The only source of 
    predictive modeling has been macroscopic models which likely do not adequately describe 
    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
    \item It will be challenging to efficiently narrow down the design space in 
    a laboratory setting.
    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
    structure which will be crucial to understanding the role of monomer structure in 
    membrane design.
    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
    \item Choice of counterion may influence the establishment of a Donnan potential 
    affecting the degree to which the membrane can exclude charged species.
    \item Moieties inside the pores may interact with neutral solutes, rejecting
    on the basis of shape and 
    %MRS: size pretty much is hydrodynamic radius
    %size, 
    interactions with specific chemical groups
rather than just hydrodynamic radius.
    %MRS: isn't this next point just a restatement of what was said at the top?
    %BJC: yes, deleted
  \end{itemize}

  Our approach to constructing a general model will be based on the development of a
  model of a specific LLC membrane which has ample experimental characterization. %BJC: ample too much?
    \begin{itemize}
	    \item We have chosen to focus on assemblies formed by Na-GA3C11
	    \item We have also narrowed our scope to the development of 
	    a model of the Col\textsubscript{h} phase membrane.
	    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
	    phase is a simpler starting point, due to the absence of water, and has
	    equivalent experimental structural data.
	    \item Despite having structural data, there is still information which 
	    experiment cannot definitively answer
    \end{itemize}

%BJC: the following just seems like filler now that I've reorganized
%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
%   a molecular model will provide evidence to answer existing and newly proposed
%   questions.
%     \begin{itemize}
%     \item Despite having structural data, there is still information which 
%     experiment cannot definitively answer
%     \end{itemize}

%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this). I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).

%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems. That is the main rationale, and it should be made clear fairly early in the introduction.  Very important to make your story absolutely as clear as possible.
%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one. I think it does a better job addressing points 2 and 3. And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)

  To further understand the nanoscopic structure of these membranes, there
  are several key questions which we intend to answer and will be laid out 
  and numbered in subsequent paragraphs.

  (1) Do monomers partition into and persist as defined monomer layers?
  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
  thought to be composed of monomer layers stacked on top of each other. 
  \begin{itemize}
  	\item Their existence is supported by experimental evidence of strong 
	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
	membrane plane.
	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
	leaves no description of what is happening in monomer tail region
	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
	\item (1) Do monomers partition into and persist as defined monomer layers?
  \end{itemize}

  (2) If layers do exist, how many monomers constitute a single layer?
  There has been no definitive answer to the question in literature.
%   We do not know the number of monomers that constitute the layers which stack
%   on top of each other to create pores.
  \begin{itemize}
%     \item The Col\textsubscript{h} phase is described as having pores made of
%     disks or layers stacked on top of one another, each containing a set 
%     number of monomers. 
    \item A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model has the best chance of directly answering this question.
  \end{itemize}
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how

    (3) How do monomers in each layer position themselves with respect to surrounding 
    layers?
%     Even if we knew the number of monomers in each layer, we still would not know how 
%     monomers in each layer are positioned with respect to other layers. 
    \begin{itemize}
      \item A driving force of self assembly in this system is thought to be $\pi$-$\pi$
      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
    \end{itemize}

%     \item While we might be able to provide answers to these questions using a 
%     molecular model, there remains the possibility that there is more than one 
%     metastable state associated with a given LLC system.

  (4) Can the system exist in other metastable states or phases that are not
  accessed during experiments?
  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item Simulating a membrane atomistically will require many atoms which further
    limits the timescales acessible with MD
    \item It is reasonable to expect that we will generate configurations which 
    are kinetically trapped in a metastable free energy basin
    \item We must be able to identify which state is produced experimentally
  \end{itemize}

  We must show that the developed molecular model is consistent with
  physical observations so that we can rely on conclusions drawn about
  structural features characteristic of the system.
  \begin{itemize}
    %MRS: main finding shouldn't be the model, but the things learned from the model. New suggestion below.
    %\item This article will illustrate the development of a predictive molecular model 
    %and the steps taken to ensure it mimics the real system within the constraints 
    %inherent to MD.
    \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
    than has ever previously been done, and explore what new structural information can be gained
    and what structure hypotheses are supported by this model.

    %MRS: this is kind of understood -- rephrasing?
    %\item To understand how physically realistic the model is, validation by comparison
    %to experiment is necessary. 
    \item We validate the model using as much experimental information as possible.
    \item We are %primarily 
    most interested in reproducing the 
    conclusions about structure which have been made from X-ray diffraction (XRD) 
    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
    \begin{itemize}
    %MRS: these are really supporting items to the above: put them indented.
	    \item We have comparied simulated X-ray diffraction patterns to experiment in 
	    order to match major features present in the 2D patterns.
	    \item We calculated ionic conductivity using two agreeing methods.
	    \item We examined the the influence of crosslinking on membrane structure.
    \end{itemize}
    %\item We have created a model that can be used to probe the large design space
    % available for membrane design
    \item The structure-building approach and analysis used in this paper can be readily extended
    to the H\textsubscript{II} phase and other similar LC systems.
  \end{itemize}

  \section*{Methods}

  HII monomers were parameterized using the Generalized AMBER Forcefield
  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
  assigned using tools from Openeye Scientific Software. All molecular dynamics 
  simulations were run using the latest version of Gromacs 2016. 
  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

  An ensemble of characteristic, low-energy vacuum monomer configurations
  were constructed by applying a simulated annealing process to a
  parameterized monomer.
  \begin{itemize}
    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
    % MRS: how chosen? randomly? be precise
    % BJC: added randomly to bullet point below
    \item A low energy configuration was randomly pulled from the trajectory
    and charges were reassigned using the am1bccsym method of molcharge
    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
    \item Using the new charges, the monomer system was annealed again and monomer
    configurations were pulled from the trajectory to be used for full
    system construction (Figure~\ref{fig:python}a).
  \end{itemize}

  The timescale for self assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic
  simulation, calling for a more efficient way to build the system. 
  \begin{itemize}
    \item Previous work has shown a coarse grain model self assemble into
    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
    \item We attempted atomistic self-assembly by packing monomers into a box 
    using Packmol \cite{martinez_packmol:_2009}.
    \item Simulations of greater than 100 ns show no indicators of progress 
    towards an ordered system.
    \item To bypass the slow self-assembly process, python scripts are used
    to assemble monomers into a structure close 
    %MRS:
    %to the expected equilibrium configuration. 
    to one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
    %\item A short, restrained equilibration, followed by NPT simulations 
    %between 400 and 500 ns, allows the initial configuration to relax into
    %an equilibrium configuration.
    %\item Our logic for choosing a starting configuration and the details
    %of the equilibration schemes are presented below.
   \end{itemize}

  We tested a number of equilibration schemes in an effort to match experiment
  while overcoming kinetic limitations of such a large system that can easily
  get stuck in multiple metastable states.
    Equilibration Scheme A:
  \begin{itemize}
    \item Apply position restraints to aromatic rings in order to maintain
    orientational order. 
    \item A short, restrained equilibration, followed by NPT simulations 
    between 400 and 500 ns, allows the initial configuration to relax into
    an equilibrium configuration.
    \item Our logic for choosing a starting configuration and the details 
    of the equilibration schemes are presented below.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
  \end{figure}

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended 
  periodically.
  \begin{itemize}
    \item Each pore is made of twenty stacked monomer layers with periodic 
    continuity in the z direction, avoiding any edge effects and creating an 
    infinite length pore ideal for studying transport.
    \item A small number of layers is preferred in order to reduce computational
    cost and to allow us to look at longer timescales.
    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
    This point will be explained in more detail later.
    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
    %BJC: so refer to supporting info here? Then put plots of diffraction data with different sized system there. I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense. And it doesn't make sense to talk about XRD this early in the methods.
  \end{itemize}

  We chose initial guesses for the remaining structural parameters based on 
  experimental data and treated them as variables during model development.
  %BJC: I could potentially break this paragraph into smaller paragraphs centered around
  % the bolded structural parameters
  %MRS Breaking into more structure is good. Short sentences, only 3-5 sentences per paragraph.

    %MRS: initial distance between pores -- we set the initial, and let it find where it wants to be
    %MRS: Or is this the initial data we COMPARE to? Be more specific about the use of these numbers. The use of the data needs to be clarified, since it's main effort here. 
  We placed pores at a chosen initial spacing, then allowed the system to settle 
  into its preferred spacing. 
  \begin{itemize}
    \item Our chosen distance between pores was based on experimental SAXS data for
    this system \cite{feng_thin_2016}.
    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
    resulting from a tightly packed initial configuration.
    \item To calculate the equilibrated pore spacing, we measured the distance between pore
    centers.
    \item Pore centers were located by averaging the coordinates of sodium ions in their 
    respective pores.
    \item Statistics were generated using the bootstrapping technique.
    %BJC: Do bootstrapping details go in supplemental?
    \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
    sampling from the original trajectory
    \item Each pore spacing has its own trajectory with its own average value
    \item The average value of each pore spacing is averaged to get the overall
    average pore spacing. 
    \item The standard deviation of average values is reported as the uncertainty in pore spacing
    % BJC: The following will go in supplemental
    \item We are interested in 5 pore-to-pore distances which should all be equal in 
    a perfect hexagonal array. Only 4 are independent  
  \end{itemize}

  %MRS: initial layer spacing.
  We chose a layer spacing based on experimental 2D WAXS data.
  \begin{itemize}  
    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
    \item Our simulations tend to equilibrate to a wider interlayer spacing of
    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
    spacings greater than 4 \angstrom~.
  \end{itemize}

  %MRS: pore radius is a different category isn't it? Is this an input piece of data?
  % should be put in a different category.
  %BJC: Well I still have to initially place the monomers some distance away from the pore
  % centers. That distance is informed by the experimental evidence.

  We based the pore radii of our initial configuration on past TEM and size exclusion 
  rejection data
  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
  of pore radius in the initial configuration.
  \begin{itemize}
    \item Experimental evidence suggests uniform pores with radii of 0.6 nm a pore radius
    \item Comparing a geometric measurement of pore size derived from an 
    atomistic model, to a less precise, experimentally derived pore size estimate,
    will give ambiguous results.
    \item What is meant by pore radius will not be clear until we have a clear picture
    of the nanoscopic pore environment.
    \item Atomistic simulations do a good job of providing the level of detail we need. The challenge
    will be to ensure that we are producing the correct picture.
    %MRS: point out this is one of the things that atomistic simulation can actually do very well - 
    % provide a clear picture of a nanoscopic environment (the questions is whether it's 
    % providing the _right_ clear picture).
    \item When constructing pores, we chose the carboxylate carbon from the monomer
    head group as a reference atom, and placed it a distance r from the pore center,
    where r is the pore radius.  %BJC: figure making that clear
    \item We will not make direct comparisons of pore radius between our model 
    and experiment to avoid the ambiguity. 
    \item However, we do define a pore radius based for our own purposes.
    \item Pore radius was measured by calculating the distance between the center of 
    mass of each aromatic ring and the center of mass of all aromatic rings in their 
    respective pores.
  \end{itemize}

  %MRS: OK, this is a variable again that we need to set. 
  The \textbf{relative interlayer orientation} was chosen based on clues from 
  diffraction data as well as the various known stacking modes of benzene 
  and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
  ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
  \begin{itemize}
    \item The T-shaped configuration was ruled out based on the inconsistency of
    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
    \item The system's preference towards the sandwiched vs. parallel displaced 
    stacking modes will be explored.
    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.  This is what we fix, this is what we leave as a variable.  The analysis probably belongs later.
    %BJC: Yeah, I will leave the rest for discussion
%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
%     suggests entropic differences based on the way the tails are able to pack.
%     \item In the sandwiched configuration, all tails start out directly on top
%     of each other which may prevent closely stacked benzene rings.
%     \item In the offset configuration, the tails are placed in between each other 
%     which may allow layers to come together in a compact way.
%     \item This difference may explain, in part, which stacking mode is more favorable.
  \end{itemize}

  We tested a number of equilibration schemes of increasing complexity in an effort
  to match experiment while overcoming kinetic limitations of such a large system 
  that can easily get stuck in multiple metastable states. All start from an initial
  configuration generated with chosen structure variables. 
  \begin{itemize}
      \item Equilibration Scheme A:
      \begin{itemize}
          \item Steepest descent energy minimization
          \item Short NPT simulation (~ 5 ns ) with berendsen barostat (tau-p = 1) at 300 K 
          \item Switch to Parrinello-Rahman (tau-p = 10) and run NPT simulation for 400 - 500 ns
          %\item Final structure strongly influenced by monomer configuration used to build 
      \end{itemize}
      \item Equilibration Scheme B:
      \begin{itemize}
          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
          configurations while allowing monomer tails to settle.
          \item Doing so also mitigates system dependence on initial monomer configuration.
          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
          \item Every 50 ps, we reduce the force constants by the square root of its
          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
          slowly released until there is no more restraining potential.
          \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
          ensemble for 400 - 500 ns in the same way as Scheme A.
      \end{itemize}
      \item Equilibration Scheme C:
      \begin{itemize} 
          \item A system equilibrated according to scheme B is cut in half so we can access
          longer simulation timescales
          \item The system is simulated at 335K, close to its isotropic transition temperature, for 200 ns. % BJC: not entirely sure if it needs to be an already equilibrate structure
          \item The structure is then linearly cooled back down to 300 K over 500 ns. 
          \item The system size is doubled back to its original size and equilibrated for 200 ns at 300 K.
          \item Tried with and without an applied electric field.
      \end{itemize}
      \item Equilibration Scheme D:
      \begin{itemize}
          \item Even in the near dry Col\textsubscript{h} system, there exists an
          equilibrium concentration of water.
          \item The hydrogen bonding network formed by the water may play a role 
          in structuring the pore.
          \item We obtained an estimate of equilibrium pore water content by solvating
          an initial configuration with water baths above and below the membrane. 
	  \item We ran the solvated system according to Scheme A but for 1000 ns
          \item Using that number we added water to the pores of an initial 
	  configuration and equilibrated according to scheme B. 
      \end{itemize}
      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1
  \end{itemize}

%  An equilibration scheme with position restraints placed on aromatic rings
  %MRS: 
  %prevents 
%  during early equilibration steps is required to prevent high energy repulsions .
  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
  %BJC: 'high energy repulsions' ?
%  \begin{itemize}
%    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
%    configurations while allowing monomer tails to settle.
%    \item Doing so also mitigates system dependence on initial monomer configuration.
%    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
%    \item Every 50 ps, we reduce the force constants by the square root of its 
%    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
%    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
%    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
%    restraining potential.  
%    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
%    ensemble for 400 - 500 ns.
   %BJC: I will reference an equilibration script that can be released with the supplemental info
   %MRS: we should release as many scripts as is feasible, can be in a github repository.
   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
%  \end{itemize}

  %BJC: the following paragraph will be replaced with something that Joe writes
  %MRS: sounds good.

  % The following methodology is taken from the 2014 Feng et al. paper where
  % WAXS is reported. The data we are using comes from the 2016 paper which 
  % I assume used the same set up but I will need to verify this with Xunda
  % before this gets sent out. The SAXS is the same as shown in the 2016 paper
  % however I will likely reproduce it with matplotlib 
  Experimental wide angle X-ray scattering measurements were performed using a 
  Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
  ($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
  calibrations of the resultant 2-D WAXS patterns were done by using a 
  silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
  patterns were integrated into 1-D plots of scattering intensity (I) versus
  q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
  2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.

  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.
  \begin{itemize}
    \item All atomic coordinates were simulated as gaussian spheres of electron
    density corresponding to each atom's atomic number.
    \item A three dimensional fourier transform (FT) of the array of electron 
    density results in a three dimensional structure factor which represents
    the unit cell in reciprocal space.
   % \item We perform an angular average of the structure factor about the 
    z axis to generate a 2D cross section close to what one would see 
    experimentally.
    \item We matched experimental 2D WAXS patterns by iterative improvement
    of our choice of initial structure and equilibration procedure.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{figure}[ht]

\begin{subfigure}{.83\linewidth}
	\centering
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth, trim={2.5cm 0 4cm 2cm}, clip]{WAXS_raw.png}%
		\caption{}~\label{fig:raw_waxs}	
	\end{subfigure}%
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_offset.png}
		\caption{}~\label{fig:rz_offset}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_layered.png}
		\caption{}~\label{fig:rz_layered}
	\end{subfigure}%
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_disordered.png}
		\caption{}~\label{fig:rz_disordered}
	\end{subfigure}
\end{subfigure}%
\begin{subfigure}{0.14\linewidth}
	\centering
	\vspace{-1cm}
	\includegraphics[width=\linewidth]{colorbar_jet.png}
\end{subfigure}
\caption{(a) Experimental 2D WAXS data contains 5 major reflections which we aim to match. The remaining 
three images are diffraction patterns simulated from MD trajectories. (b) The parallel displaced
configuration gives rise to all reflections of interest. (c) The sandwiched configurations gives rise to a
pattern with all major reflections except R-helix. R-spots is strong relative to R-alkanes in comparison
to the parallel displaced configuration. (d) The disordered pore configuration creates a pattern with only
R-alkanes and R-pores in common with experiment}~\label{fig:xrd}
\end{figure}
